---
title: "HuaYangProblemSet4"
author: "Hua Yang"
date: "2022-10-29"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GBA 5140 Statistics Essentials for Business Analytics
## Problem Set 4
## Sampling & Sampling Distributions


Problem 1 (Use R Version: 4.0.0+)
Load “Data-SouthGermanCredit.csv” into RStudio. Write R code for the following tasks. Post your R code and RStudio output (console output) below each task.

 ```{r }
SGC.df <- read.csv("Data-SouthGermanCredit.csv")
head(SGC.df)
```

**1.Compute population mean and population standard deviation of variable “amount”.**
```{r mtcars_df}
mu<-mean(SGC.df$amount)
print(paste("Population mean of amount:",mu))
N<-dim(SGC.df)[1]
sigma<-sqrt((N-1)/N)*sd(SGC.df$amount)
print(paste("Population standard deviation of amount:",sigma))
```

**2.Compute population proportion of variable “telephone” that takes value “yes (under customer name)”.**

```{r }
p<-sum(SGC.df$telephone=="yes (under customer name)")/N
print(paste("Population proportion of telephone that takes value in yes (under customer name)",p))
```

 

**3.Use “1500” as seed, extract a sample of 30 observations from the population, and display the row numbers in the sample. (Hint: use row.names function to access row number, which can be used as an “ID” for each observation)**

```{r}
n<-30
set.seed(1500)
creditSample<-sample(row.names(SGC.df),n,replace = FALSE)
creditdfSample<-SGC.df[match(creditSample,row.names(SGC.df)),]
```

 

**4.Compute the sample mean and sample standard deviation of variable “amount”.**
```{r}
x.bar<-mean(creditdfSample$amount)
print(paste("Sample mean of amount:",x.bar))
s<-sd(creditdfSample$amount)
print(paste("Sample standard deviation of amount:",s))
```
**5.Compute the sample proportion of variable “telephone” that takes value “yes (under customer name)”.**
```{r}
p.bar<-sum(creditdfSample$telephone=="yes (under customer name)")/n
print(paste("Sample proportion of telephone that takes value in yes (under customer name)",p.bar))
```

**6.Compute the standard error of sample mean of variable “amount”.**
```{r}
if(n/N<0.05){
  x.bar.se<-sigma/sqrt(n)
}else{
  x.bar.se<-sqrt((N-n)/(N-1))*sigma/sqrt(n)
}
print(paste("Sample mean standard error:",x.bar.se))
```
**7.Compute the standard error (with normal approximation) of sample proportion of variable “telephone” that takes value “yes (under customer name)”.**
```{r}
if(n/N<0.05){
  p.bar.se<-sqrt(p*(1-p)/n)
}else{
  p.bar.se<-sqrt((N-n)/(N-1))*sqrt(p*(1-p)/n)
}
print(paste("Sample proportion standard error:",p.bar.se))
```