---
title: "HuaYangProblemSet5"
author: "Hua Yang"
date: "2022-10-30"
output:
  word_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GBA 5140 Statistics Essentials for Business Analytics
## Problem Set 5
## Interval Estimation


Problem 1
Costs are rising for all kinds of medical care. The mean monthly rent at assisted-living facilities was reported to have increased 17% over the last five years to $3486 (The Wall Street Journal, October 27, 2012). Assume this cost estimate is based on a sample of 120 facilities and, from past studies, it can be assumed that the population standard deviation is $650. Write R code for the following tasks. Post your R code and RStudio output (console output) below each task.


 ```{r }

```

**1.Develop a 95% confidence interval estimate of the population mean monthly rent.**
```{r }
n<-120
x.bar<-3486
sigma<-650
alpha<-1-0.95
z<-qnorm(1-alpha/2,mean=0,sd=1,lower.tail = TRUE)
x.bar.se<-sigma/sqrt(n)
print(paste("Interval estimate lower bound:",x.bar-z*x.bar.se))
print(paste("Interval estimate upper bound:",x.bar+z*x.bar.se))
```

Problem 2
According to statistics reported on CNBC, a surprising number of motor vehicles are not covered by insurance. Sample results, consistent with the CNBC report, showed 46 of 200 vehicles were not covered by insurance. Write R code for the following tasks. Post your R code and RStudio output (console output) below each task.


```{r }

```

 

**1.Develop a 95% confidence interval for the population proportion.**

```{r}
n<-200
p.bar<-46/n
alpha<-1-0.95
z<-qnorm(1-alpha/2,mean=0,sd=1,lower.tail = TRUE)
p.bar.se<-sqrt(p.bar*(1-p.bar)/n)
print(paste("Interval estimate lower bound:",p.bar-z*p.bar.se))
print(paste("Interval estimate upper bound:",p.bar+z*p.bar.se))
```

Problem 3
Write R code for the following tasks. Post your R code and RStudio output (console output) below each task.

```{r}

```
**1.How large a sample should be selected to provide a 95% confidence interval with a margin of error of 10? Assume that the population standard deviation is 40.**
```{r}
sigma<-40
alpha<-1-0.95
E<-10
z<-qnorm(1-alpha/2,mean=0,sd=1,lower.tail = TRUE)
print(paste("The minimum sample size should be:",(z^2)*(sigma^2)/(E^2)))
```


Problem 4 (Use R Version: 4.0.0+)
Load “Data-SouthGermanCredit.csv” into RStudio. Write R code for the following tasks. Post your R code and RStudio output (console output) below each task.

```{r}
setwd('/Users/xiaoqin/Documents/Business Analytics/5140/week9')
sgc_df<-read.csv("Data-SouthGermanCredit.csv")
head(sgc_df)
```
**1.Use “1100” as seed, extract a sample of 40 observations from the population, and display row numbers in the sample.**
```{r}
n<-40
set.seed(1100)
southSample<-sample(row.names(sgc_df),n,replace = FALSE)
southdfSample<-sgc_df[match(southSample,row.names(sgc_df)),]
southSample
```
**2.Compute the sample mean and sample standard deviation of variable “amount”.**
```{r}
x.bar<-mean(southdfSample$amount)
print(paste("Sample mean of amount:",x.bar))
s<-sd(southdfSample$amount)
print(paste("Sample standard deviation of amount:",s))
```
**3.Compute the sample proportion of variable “telephone” that takes value “yes (under customer name)”.**
```{r}
p.bar<-sum(southdfSample$telephone=="yes (under customer name)")/n
print(paste("Sample proportion of telephone that takes value in yes (under customer name)",p.bar))
```
**4.Develop a 95% confidence interval for the sample mean of variable “amount”, assuming we don’t know population standard deviation of “amount”.**
```{r}
n<-dim(southdfSample)[1]
x.bar<-mean(southdfSample$amount)
s<-sd(southdfSample$amount)
alpha<-1-0.95
t<-qt(1-alpha/2,df=n-1,lower.tail = TRUE)
x.bar.se<-s/sqrt(n)
print(paste("Interval estimate lower bound:",x.bar-t*x.bar.se))
print(paste("Interval estimate upper bound:",x.bar+t*x.bar.se))
```

**5.Develop a 95% confidence interval for the sample proportion of variable “telephone” that takes value “yes (under customer name)”.**
```{r}
n<-dim(southdfSample)[1]
p.bar<-sum(southdfSample$telephone=="yes (under customer name)")/n
alpha<-1-0.95
z<-qnorm(1-alpha/2,mean=0,sd=1,lower.tail = TRUE)
p.bar.se<-sqrt(p.bar*(1-p.bar)/n)
print(paste("Interval estimate lower bound:",p.bar-z*p.bar.se))
print(paste("Interval estimate upper bound:",p.bar+z*p.bar.se))
```